Bioverse: Origins of Life

### 2023-12-16 src/tex/ms.tex
add 3-param evidence grid

>>>>

The expected resulting evidence further depends on the a priori unknown abiogenesis rate $f_\mathrm{life}$ and on the \gls{NUV} flux threshold.
\begin{figure*}
    \script{semian_true_evidence.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/semian_evidence-grid.pdf}
        \caption{Probability of obtaining true strong evidence for different abiogenesis rates, \gls{NUV} flux thresholds, and sample sizes. For each of these parameters, higher values increase the probability of yielding strong evidence.}
        \label{fig:semian_evidence-grid}
    \end{centering}
\end{figure*}
Figure~\ref{fig:semian_evidence-grid} illustrates this dependency: For very low values of either parameter, samples drawn under the null or alternative hypotheses are indistinguishable and the Bayesian evidence is always low.
Both higher $f_\mathrm{life}$ and higher \gls{NUV} flux thresholds increase the probability of obtaining strong evidence.
Larger sample sizes enable this at lower values of these parameters.
